Sensitivity Analysis

### 2024-05-22 Article_Sensitivity_Analsysis_short-Chamomile.tex
Updates from Overleaf

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study aimed to investigate the supercritical extraction process of caraway oil from chamomile flowers. The distributed-parameter model describes the fluid-solid extraction process. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated from the Peng-Robinson equation of state. A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s. Sensitivity analyses play a crucial role in assessing the robustness of the findings or conclusions based on mathematical model. The local sensitivity analysis investigates the influence of infinitely small changes in the inlet temperature, pressure, and flow rate on the extraction yield.

@@

\clearpage \appendix \label{appendix}
\section{Appendix}

%\subsection{Thermodynamic}
\subfile{Sections/Qubic_EOS} \label{CH: EOS}

\subsection{Cardano's Formula} \label{CH: Cardano}
\subfile{Sections/Cardano}

>>>>

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
The article presents a comprehensive study on the supercritical fluid extraction of essential oil from chamomile flowers, focusing on model dynamics and applying a distributed-parameter model to describe the fluid-solid extraction process. By employing the concept of quasi-one-dimensional flow, the study simplifies the spatial dimensions of the extraction process, ensuring uniform flow across any cross-section while allowing for variations in the area available for the fluid phase. The physical properties of the solvent are estimated using the Peng-Robinson equation of state. The model was validated under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s. The model dynamic is investigated by analysing how sensitive the model output is to model parameters. In this work, the local sensitivity analysis is introduced and used to examine the influence of infinitely small changes in the pressure on the state space and the extraction yield.

@@

%\clearpage \appendix \label{appendix}
%\section{Appendix} 
%\subfile{Sections/Qubic_EOS} \label{CH: EOS}
%\subsection{Cardano's Formula} \label{CH: Cardano}
%\subfile{Sections/Cardano}

### 2024-05-22 Sections/Literature_Review.tex
Updates from Overleaf

	This study aims to analyse the influence of changes in operating conditions on the supercritical extraction process described in {\color{red}article 1}. The emphasis is put on the effect of the mass flow rate, pressure, and the inlet temperature. The relation between input and output is obtained by applying a sensitivity analysis. Sensitivity analysis examines the impact of varying inputs or model parameters on the system's output. The aim is to understand and allocate the source of uncertainty in the output to the corresponding inputs or parameters. There are many sensitivity analysis methods, which include but are not limited to those listed below:

@@

	Different supercritical extraction models were analysed using sensitivity analysis. \citet{Fiori_2007}, performed the sensitivity calculations by varying the parameters within their confidence interval and observing how the model results changed. This allows to evaluate the effect of the uncertainties on model predictions. The sensitivity analysis revealed that the particle diameter and the internal mass transfer coefficient are significant for the extraction process. The effect of changing some operative conditions was also investigated, underlining how the solvent flow rate and the seed milling affect the extraction process.

	\citet{Santos2000}, in their work, considered a model of supercritical extraction process for semi-continuous isothermal and isobaric extraction process using carbon dioxide as a solvent. The parametric sensitivity analysis was carried out by applying disturbances of 10\% in the values of the normal operation conditions.

	\citet{Hatami2024} used a one-factor-at-a-time sensitivity analysis to assess the response of NPV concerning variations in both technical and economic variables. Their findings show that the most influential factors on NPV include the price of the extract, the interest rate, the dynamic time of SFE, and the project lifetime.

	\citet{Poletto1996} provided a general dimensionless model for the supercritical extraction process of vegetable and essential oils and applied a sensitivity analysis. They found that a dimensionless partition coefficient and a dimensionless characteristic time appeared as the most important parameters of the extraction process. The sensitivity calculations were performed by varying the parameters and analysing the model response.

>>>>

	This study aims to analyse the influence of changes in operating conditions on the supercritical extraction model described in {\color{red}article 1}. The relation between input and output is obtained by applying a sensitivity analysis. Sensitivity analysis examines the impact of varying inputs or model parameters on the system's output. The aim is to understand and allocate the source of uncertainty in the output to the corresponding inputs or parameters. There are many sensitivity analysis methods, which include but are not limited to those listed below:

@@

	Different supercritical extraction models were analysed using sensitivity analysis. \citet{Fiori_2007}, performed the sensitivity calculations by varying the parameters within their confidence interval and observing how the model results changed. This allows to evaluate the effect of the uncertainties on model predictions. The sensitivity analysis revealed that the particle diameter and the internal mass transfer coefficient are the most influential factors in the extraction process. The effect of changing operating conditions was also investigated, underlining how solvent flow rate and seed milling affect extraction.

	In the work of \citet{Santos2000}, a diffusive model for the semi-continuous, isothermal, and isobaric extraction process is analysed by a parametric sensitivity analysis using a factorial design in two levels. The parametric sensitivity analysis was carried out by applying disturbances of 10\% in the values of nominal values of velocity, particle diameter, and initial concentration in the solid and liquid phases. The authors concluded that it is necessary to determine the optimum particle diameter and manipulate the solvent superficial velocity to control the process.

	\citet{Hatami2024} used a one-factor-at-a-time sensitivity analysis and employed two distinct strategies to conduct their analysis: the first strategy involved applying an equal fluctuation to all technical and economic parameters, while the second strategy utilised real ranges for fluctuating these parameters. The authors found that the most influential factors on NPV include the price of the extract, the interest rate, the dynamic time of SFE, and the project lifetime. Moreover, in this study tried to determine rhe upper and lower bounds for technical and economic factors, utilizing pertinent literature data.

	\citet{Poletto1996} provided a general dimensionless model for the supercritical vegetable and essential oils extraction process and applied a sensitivity analysis. They found that a dimensionless partition coefficient and a dimensionless characteristic time are the most influential parameters of the extraction process. The sensitivity calculations were performed by varying the parameters and analysing the model response.

### 2024-05-22 Sections/Model.tex
Updates from Overleaf

			The pressure term in the energy equation, given by Equation \ref{EQ:Enthalpy_equation}, describes the change of the thermodynamic pressure with respect to time. As explained in Chapters \ref{CH:Governing_equations_chapter}, at Low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound. Under such conditions, the term $\partial P/\partial t$ can be approximated by an difference equation, which describes the change of pressure in the whole system. The pressure ($P$) in the system is considered a state variable, while the pressure in the new time-step ($P_{in}$) is considered a control variable.

			Such a simplified equation takes into account the pressure change in the energy balance, but the dynamics are simplified and do not consider the effects of pressure losses. In a real system, the dynamics of pressure change would depend on a pump used in an extraction system, as well as a back-pressure regulator used to control an outlet valve.

@@

			{\footnotesize
				\begin{equation}
					\underbrace{h\left(t,x\right)}_{\text{Heat balance}}=\underbrace{h\left(T,P,\rho_f\left(T,P\right)\right)}_{\text{Departure function}}
					\label{EQ:Enthalpy_root}
				\end{equation}
			}

>>>>

@@

			{\footnotesize
				\begin{equation}
					\min_T \left( \underbrace{h\left(t,x\right)}_{\text{Heat balance}} - \underbrace{h\left(T,P,\rho_f\left(T,P\right)\right)}_{\text{Departure function}} \right)^2
					\label{EQ:Enthalpy_root}
				\end{equation}
			}

			The pressure term in the energy equation, given by Equation \ref{EQ:Enthalpy_equation}, describes the change of the thermodynamic pressure with respect to time. As explained in Chapters \ref{CH:Governing_equations_chapter}, at Low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound. Under such conditions, the term $\partial P/\partial t$ can be approximated by a difference equation, which describes the pressure change in the whole system. The pressure ($P$) in the system is considered a state variable, while the pressure in the new time-step ($P_{in}$) is considered a control variable.

			Such a simplified equation allows for instantaneous pressure change in the system but does not consider a gradual pressure build-up and the effects of pressure losses. In a real system, the dynamics of pressure change would depend on a pump used in an extraction system and a back-pressure regulator used to control an outlet valve.
